---
title: "A22_Pair12"
output: pdf_document
---
#A22_Pair12
##Build a neural network for the Manheim data with a range of hidden layers and decide which model gives the best fit.
```{r}
library(dplyr)
library(readr)
library(neuralnet)
library(ggplot2)
library(Metrics)

t <- read_csv("/Users/apple/Downloads/manheim.csv")

# First fit a glm
lm <- lm(price ~ miles + sale + model, data = t)
summary(lm)
predict.lm <- round(predict(lm),0)
MSE.lm <- rmse(t$price,predict.lm)

```

```{r}
# Recoding
t$saleCode <- case_when(
  t$sale == 'Auction' ~1,
  t$sale == 'Online' ~2
  )
t$modelCode <- case_when(
  t$model == 'X' ~1,
  t$model == 'Y' ~2,
  t$model == 'Z' ~3
  )
t$sale <- NULL
t$model <- NULL
t

```

```{r}
# Normalize data
maxs <- apply(t, 2, max)
mins <- apply(t, 2, min)
n <- as.data.frame(scale(t, center = mins, scale = maxs - mins))
```

```{r}
# Build neural net
set.seed(2)

for(i in 2:10){net <- neuralnet(price ~ miles + saleCode + modelCode, data = n, hidden
= i, linear.output = T)
pr.net <- compute(net, n[,2:4])
# rescale
predict.net <- pr.net$net.result*(max(t$price)-min(t$price))+min(t$price)
MSE.net <- rmse(t$price, predict.net)
 }
plot(net)
```

```{r}
 # Compare the two models' mean square error
paste('MSEs for linear regression and neural net ',round(MSE.lm,
0),round(MSE.net,0))
paste('Percent difference ', round(((MSE.net - MSE.lm)/MSE.lm*100),2))
```
## Compare your result with a general linear model.
```{r}
# Graph the findings - -------------
t <- t %>% mutate(diff = predict.lm - predict.net)
ggplot(t, aes(x=price)) +
  geom_point(aes(y=diff, color='Prediction difference')) +
  geom_point(aes(y=predict.lm, color='Linear model')) +
  geom_point(aes(y=predict.net,color='Neural net')) +
  geom_abline(intercept = 0, slope = 1) +
  xlab('Actual price') +
  ylab('Predicted price')
```

##Analysis: The model with 2:10 hidden layers showed a 1415 value of linear regression and 1325 value of neural net. The neutral net is smaller than linear regression. Therefore this model is useful to predict price.